---
title: "This package has been used in my statistics class"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{This package has been used in my statistics class}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL224753darr0006)
```

# Introduction

This is that package that I used throughout MATH 4753. This package contains .R functions that were used throughout the course. It also contains some data that was used as well.

Here is the link to my github repository:
https://github.com/HunterDarr/MATH4753

# Testing my package functions

## 1 myboot2

```{r}
sam=round(rnorm(20,mean=10,sd=4),2)
noOutPut = FALL224753darr0006::myboot2(x=sam,fun="median", xName = "median")
```

The myboot2 function was used in lab 9. The function is used to make point and interval estimates along with an output as a list. 

## 2 mycltu

```{r}
FALL224753darr0006::mycltu(n=54,iter=100000)
```

The mycltu function was used in lab 8. It is used to represent the central limit theorem.

## 3 mymaxlik

```{r}
logbin2=function(x,param) log(dbinom(x,prob=param,size=20)) #With size set to 20 for 20 trials each
FALL224753darr0006::mymaxlik(x=c(3,3,4,3,4,5,5,4),param=seq(0,1,length=1000),lfun=logbin2)
```

The mymaxlik function was used in lab 10. Its purpose is to make maximum likelihood estimates.

## 4 ntickets

```{r}
FALL224753darr0006::ntickets(N=400,gamma = 0.02, p = 0.95)
```

The ntickets function is my implementation of project1 in this course. Its purpose is to estimate the number of tickets to be sold on a flight for booking. Airlines want to oversell flights because passengers often do not show up. This allows them to find the number of tickets to sell to have a full plane while keeping the probability of having too many passengers for the flight low.

## Other

There are more functions contained in this package under the R folder.

# My packaged data working

```{r}
head(FALL224753darr0006::fire)
```

The data I have packed is the fire data. You can see the head() of it above.

# devtools::check() output

── R CMD check results ─────────── FALL224753darr0006 0.1.0 ────
Duration: 14.2s

0 errors ✔ | 0 warnings ✔ | 0 notes ✔

R CMD check succeeded
